Practical Optional Types for Clojure

### 2015-02-21 intro.tex
add opening example to tests

\begin{figure}
\begin{minted}[]{clojure}
(ann parent [(U nil File) -> (U nil File)])
(defn parent [^File f]
  (when f
    (let [s (.getParent f)]
      (assert s "Expected parent string, got nil")
      (new File s))))
\end{minted}
\caption{A simple Typed Clojure program}
\label{fig:ex1}
\end{figure}
Figure~\ref{fig:ex1} presents a simple program demonstrating several
aspects of our system, from simple type annotations to explicit
handling of Java's \texttt{null} in interoperation, as well as an
extended form of occurrence typing and Clojure's \emph{type hints},
which are central to Typed Clojure's approach to interoperability.

>>>>

\begin{figure}
\inputminted[firstline=5,lastline=10]{clojure}{code/demo/src/demo/parent.clj}
\caption{A simple Typed Clojure program}
\label{fig:ex1}
\end{figure}

Figure~\ref{fig:ex1} presents a simple program demonstrating several
aspects of our system, from simple type annotations to explicit
handling of Java's \texttt{null} in interoperation, as well as an
extended form of occurrence typing and Clojure's \emph{type hints},
which are central to Typed Clojure's approach to interoperability.
